SunPy - Python for Solar Physics

### 2014-08-28 3-1-VSO.tex

Listing~\ref{code:vso_query_simple} shows an example of how to query and download data using
from the VSO using the \texttt{vso} module.
Queries are constructed using one or more attribute objects. Each
attribute object is a constraint on a parameter of the data set, such as the
time, instrument, or wavelength.
Listing~\ref{code:vso_query_simple} also shows how to download the data using
the constructed query. The path to which the data files will be downloaded is defined using custom tokens
which reference the file metadata (e.g., instrument, detector, filename). This provides
users the ability to organize their data into subdirectories on download.

>>>>

Listing~\ref{code:vso_query_simple} shows an example of how to query and download data
from the VSO using the \texttt{vso} module.
Queries are constructed using one or more attribute objects. Each
attribute object is a constraint on a parameter of the data set, such as the
time of the observation, instrument, or wavelength.
Listing~\ref{code:vso_query_simple} also shows how to download the data using
the constructed query. The path to which the data files will be downloaded is defined using custom tokens
which reference the file metadata (e.g., instrument, detector, filename). This provides
users the ability to organize their data into subdirectories on download.
